Tables

### 2021-08-27 results/tables/biomass&numbers.Rmd
revised

all = rbind(old, y19, y20)
all = all %>% mutate(year = as.numeric(str_sub(調査種類名称, 1, 4)), NS = str_sub(南北, 1, 1)) %>% dplyr::rename(data = "尾数・重量", sp = "和名", sum = "資源量計") %>% select(year, NS, data, sp, sum)
ns = data.frame(NS = c("N", "S"), 南北 = c("北部", "南部"))
all = left_join(all, ns, by = "NS") %>% select(-NS) %>% dplyr::rename(NS = 南北)
all$NS = factor(all$NS, levels = c("北部", "南部"))
all = all %>% mutate(data = ifelse(all$data == "資源重量", "重量", "尾数"))
unique(all$sp)
sp_list = unique(all$sp)
levels(sp_list)
sp_list = factor(sp_list, levels = c())

biomass = all %>% filter(data == "重量") %>% dplyr::group_by(year, sp) %>% dplyr::summarize(total = sum(sum))
numbers = all %>% filter(data == "尾数") %>% dplyr::group_by(year, sp) %>% dplyr::summarize(total = sum(sum))

for(i in 1:length(sp_list)){
  assign(paste(mass, ))
}

@@

#### 現存量
```{r biomass}
for(i in 1:length(sp_list)){
  biomass = all %>% filter(data == "重量", sp == sp_list[i]) %>% dplyr::group_by(year, sp) %>% dplyr::summarize(total = sum(sum))
  biomass
}
```

#### 現存尾数
```{r numbers}
all %>% filter(data == "尾数") %>% dplyr::group_by(year, sp) %>% dplyr::summarize(total = sum(sum))
```

>>>>

all = rbind(old, y19, y20)
all = all %>% mutate(year = as.numeric(str_sub(調査種類名称, 1, 4)), NS = str_sub(南北, 1, 1)) %>% dplyr::rename(data = "尾数・重量", sp = "和名", sum = "資源量計") %>% select(year, NS, data, sp, sum)
ns = data.frame(NS = c("N", "S"), 南北 = c("北部", "南部"))
all = left_join(all, ns, by = "NS") %>% select(-NS) %>% dplyr::rename(NS = 南北)
all$NS = factor(all$NS, levels = c("北部", "南部"))
all = all %>% mutate(data = ifelse(all$data == "資源重量", "重量", "尾数"))
unique(all$sp)
sp_list = unique(all$sp)
# levels(sp_list)
# sp_list = factor(sp_list, levels = c("スケトウダラ０＋", "スケトウダラ１＋", "マダラ０＋", "マダラ１＋", "マダラ２＋", "イトヒキダラ",  "キチジ", "ズワイガニ雌", "ズワイガニ雄", "スルメイカ", "ベニズワイ雌", "ベニズワイ雄", "アカガレイ", "サメガレイ", "ババガレイ",  "キアンコウ"))

biomass = all %>% filter(data == "重量") %>% dplyr::group_by(year, sp) %>% dplyr::summarize(トン = sum(sum)/1000) %>% dplyr::rename(年 = year, 魚種 = sp)
numbers = all %>% filter(data == "尾数") %>% dplyr::group_by(year, sp) %>% dplyr::summarize(千尾 = sum(sum)/1000) %>% dplyr::rename(年 = year, 魚種 = sp)

for(i in 1:length(sp_list)){
  assign(paste("mass", i, sep = ""),
         biomass %>% filter(魚種 == sp_list[i])
         )
}

for(i in 1:length(sp_list)){
  assign(paste("n", i, sep = ""),
         numbers %>% filter(魚種 == sp_list[i])
         )
}

@@

### 現存量
```{r biomass, echo=F}
mass1
mass2
mass3
mass4
mass11
mass5
mass6
mass12
mass13
mass7
mass14
mass15
mass8
mass9
mass10
mass16
```

### 現存尾数
```{r numbers, echo=F}
n1
n2
n3
n4
n11
n5
n6
n12
n13
n7
n14
n15
n8
n9
n10
n16
```
